Stay in shape! Homework exam II

### 2016-04-04 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
did the bonus and the storage of 3

\section{Voronoi nearest neigbour\emph{s}}
\subsection{Storage}
\subsection{Query time}
%TODO: wtf? maybe with higher order voronoi?? But it won't be log n
%TODO: we hebben ook bogen. Kun je representateren als een lijn en een punt.

>>>>

\subsection{Bonus}
Applying what we've learned above we know we can handle ranges by using
binary trees. For single values we can use interval trees.
So suppose we know that $X$ will be an interval. Then the main tree will
be a binary tree sorting on $x$ where each node has a two sub-binary trees $y$
and $z$.
When we start reporting for x we'll choose the associated subtree which
is the interval qeury.
If $Y$ is an interval then we choose the $y$ subtree.
In the $y$ tree nodes have ascsociated structures that are interval trees
on $z$.
If $Z$ is the interval then we choose the $z$ subtree. In $z$ subtree
there is again an associated structure for each node which is an interval
tree on $y$.
We can create another structure for when $X$ is not an interval. Similiar
to the one above so that we can handle any range query.

The storage requirement is:

\[O(n\cdot log^2(n))\]

Because the main tree is amplified aditionally in size by an extra associated
structure depth.
The query time is:

\[ O(log^3(n)+r) \]

Because there are 3 trees to traverse and we still need to report the anwsers.
\section{Voronoi nearest neigbour\emph{s}}
\subsection{Storage}
The original datastructure was already of order:

\[O(n)\]

storage, this was a given, now we will start analyising how the extension
will impact this order.
For every point $p$ we store a trapazoidal map, which is $O(n)$ size
storage (Theorom 6.3 of the book \cite{book}) where $n$ equals the amount of
voronoi neighbours $k_p$. So per point we now have a storage of the order:

\[O(1+k_p)\]

However we can put an expectation on $k_p$ by using theorom 7.3 of the book
\cite{book}. It says the number of edges is at most $3n-6$, an edge is a
division between neigbours so the expected amount of neigbours per point
is $3$. So the expected storage complexity is:

\[ O(3n) = O(n) \]
\subsection{Query time}
